Paper_stuff

### 2023-09-30 Paper_stuff.Rmd
filter pre > 20

df

Mothership_post$ID1
RCI_df_dep <- Mothership_post |>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUDOS_pre),
    post = as.numeric(CUDOS_post),
    Disorder = Disorder_treat
  ) |>
  select(
    ID1,pre,post,Disorder
  ) |>
  filter(!is.na(pre),
         !is.na(post))

RCI_df_anx <- Mothership_post |>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUXOS_pre),
    post = as.numeric(CUXOS_post),
    Disorder = Disorder_treat
  ) |>
  select(
    ID1,pre,post,Disorder
  ) |>
  filter(!is.na(pre),
         !is.na(post))

>>>>

RCI_df_dep <- Mothership_post |>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUDOS_pre),
    post = as.numeric(CUDOS_post),
    Disorder = Disorder_treat
  ) |>
  select(
    ID1,pre,post,Disorder
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

RCI_df_anx <- Mothership_post |>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUXOS_pre),
    post = as.numeric(CUXOS_post),
    Disorder = Disorder_treat
  ) |>
  select(
    ID1,pre,post,Disorder
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)
